---
title: "R Notebook"
output: 
---

```{r setup, echo = F, warning=F, message=F}
library(tidyverse)
library(knitr)

theme_set(theme_light())
db <- read_rds("bld/full-data-clean.rds")

knitr::opts_chunk$set(echo = FALSE,
                      cache = FALSE,
                      message = FALSE,
                      warning = FALSE, 
                      results = 'asis')
```


```{r}
db_sorted <- db %>% 
  select(author, year, intervention_name,  d, se_d, study_design, scale_type, everything()) %>%
  filter(!is.na(d), !is.na(se_d)) %>%
  mutate(direction = as.integer(direction),
         d = abs(as.numeric(d)),
         se_d = as.numeric(se_d)) 

#  # * direction
```


```{r}

db_sorted_rct_behavioral <- db_sorted %>%
  filter(study_design == 'rct', scale_type == 'behavior',
         d < 0, se_d < 5)

# , d < 3, se_d < 2
attach(db_sorted_rct_behavioral)
plot(d, se_d)
#plot(se_d ~ d)
abline(lm(d ~ se_d))
lm(d ~ se_d)


plot(se_d, d)
plot(se_d ~ d)
abline(lm(d ~ se_d))
lm(d ~ se_d)

```


SETH TO DO NOTES
do attitudes correlate with behaviors?
In an individual study, Y/N?
Across intervention types? 

## Also Seth -- forest plot

Main behavior plot -- 
* collapse all behavior outcomes into one and size the cirlces by number of scales that were collapsed *and* number of -- DON"T DO THIS"
* SES and IRMA -- one dot
* immediate post test -- apples to apples
* one dot per intervention
* plot with different circle types, filled in or colored based on Attitudes vs behaviors relationship and
* class of interventions AND class of dependent variables -- 
* class of intervention -- studies are multiarmed, 
* average *within stud* correlation between attitudes and behavior 
** some time has to have elapsed. 