---
title: "5-descriptives"
author: "Seth Green and Johh-Henry Pezzuto"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output:
  rmarkdown::html_document:
    smart: true
    theme: spacelab
    number_sections: no
    toc_float:
      collapsed: true
    toc_depth: 4
editor_options: 
  chunk_output_type: console
---


```{r echo=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      cache = FALSE,
                      message = FALSE,
                      warning = FALSE, 
                      results = 'markup')


library(tidyverse)
library(ggtext)
library(patchwork)
library(ggthemes)
library(ggrepel)
library(knitr) 
library(kableExtra)
library(janitor)
library(scales)
library(metafor)

source('./functions/study_count.R')
source('./functions/map_robust.R')

dat <- readRDS(file = '../data/sa_meta_data_final.rds') %>%
  mutate(
    attitudes_behaviors = case_when(
      all(c('attitudes', 'behavior') %in% scale_type) ~ 0,
      scale_type == 'attitudes' ~ 1,
      scale_type == 'behavior' ~ 2)) %>%
  ungroup()
```

# The Problem of Sexual Violence

Our present review provides empirical results from 13 countries

```{r}
length(unique(dat$country))
```


## Inclusion and Exclusion Criteria for Study Selection

Table 1 details the number of papers for each study design.

```{r}
dat |> 
  distinct(unique_paper_id, unique_study_id, study_design) |> 
  group_by(study_design) |> 
  summarise(n_papers = n_distinct(unique_paper_id),
            n_studies = n_distinct(unique_study_id)) |> 
  kable(format = "latex", booktabs = T)
```


# Overview of the Studies in the Meta-Analytic Database

The database
spans the years 1985-2018, encompassing 226 manuscripts that describe 304 studies, in which we coded 500
distinct point estimates.

```{r years_and_countries}
dat |> 
  summarise(year_min = min(year),
            year_max = max(year),
            n_manuscripts = n_distinct(unique_paper_id),
            n_studies = n_distinct(unique_study_id),
            n_point_estimates = n())
```


Overall these are relatively large studies, with an average of 403 participants and a median of 162 participants. 

```{r}
dat |> 
  group_by(unique_study_id) |> 
  summarise(mean_n_per_study = mean(n_t_post, na.rm = T) + mean(n_c_post, na.rm = T)) |>  # collapse outcomes first, so studies with more outcomes don't have more weight
  ungroup() |> 
  summarise(mean_n = mean(mean_n_per_study), # then collapse studies in estimate
            median_n = median(mean_n_per_study))
```



In addition, 30% percent of these studies test primary prevention efforts that span more than one day.

```{r}
dat |>
  distinct(unique_study_id, intervention_length) |> 
  mutate(intervention_length = ifelse(intervention_length > 1, 1, 0)) |> 
  summarise(perc_greater_1_day = mean(intervention_length, na.rm = T))
```


```{r}
tt_overall = dat |> # overall line
      group_by(year) |>
      summarise(n = n_distinct(unique_study_id)) |>
      add_row(year = 1985, n = 0)

zeitgeist = tibble(year = c(1998, 2000, 2007), 
                   n = pull(filter(tt_overall, year %in% c(1998, 2000, 2007)), n),
                   event = c("Safe dates", "Men's Program", "Bringing in\nthe Bystander"))

tt_overall     |>
  ggplot(aes(year, n)) +
  geom_line(size = 2) +
  # geom_segment(aes(x = year, ## add "flag poles"
  #                  xend = year,
  #                  y = 0,
  #                  yend = n,
  #                  label = NULL),
  #              inherit.aes = F, 
  #              linewidth = 1.5,
  #              data = zeitgeist) +
    geom_label_repel(mapping = aes(x = year, ## labels
                                   y = n,
                                   label = event),
                     size = 6,
                     segment.size	= 1.5,
                     inherit.aes = F,
                     data =  zeitgeist,
                     nudge_x = c(2, 2.5, -1.9),
                     nudge_y = c(6, 5.5, 5),
                     min.segment.length = 0, 
                     force = 0.3) +
  scale_x_continuous(
    limits = c(1985, 2018),
    breaks = c(1985, seq(1985, 2020, by = 5), 2018)
  ) +
  theme_bw() +
  theme(
    axis.text = element_text(size = 12), 
    legend.text = element_text(size = 12),
    legend.position = "bottom"
  ) +
  labs(
    x = NULL,
    y = "# of studies",
    col = NULL
  )

ggsave("results/tt_studies.pdf", height = 5)
```

We observe that 270 studies which constitute 89% of the database were conducted in the United States. The remaining 34 studies
come from various places around the world, including Canada, Europe, and Africa.


```{r}
dat |> 
  distinct(unique_study_id, country) |> 
  count(country, sort = T) |> 
  mutate(perc = n / sum(n))
```


Nearly 69% of all studies are conducted among college students. Another 13% focus on high school students, while 9% percent
focus on middle school students. Outside of the education sphere, we find that 4% of studies were conducted
in the workplace, and 2% in community settings. 

```{r}
dat |> 
  distinct(unique_study_id, setting) |> 
  count(setting, sort = T) |> 
  mutate(perc = n / sum(n))
```


In fact, 61% of the studies targeted both men and women, while 27% targeted only men, and 6% targeted only women (1% of studies did not report the gender target).
```{r}
dat |> # 
      mutate(participant_sex = ifelse(participant_sex %in% c("male and female in mixed groups", 
                                                             "male and female with group composition not specified", 
                                                             "male and female in separate groups"), 
                                      "mixed gender groups", 
                                      participant_sex)) |>
      distinct(unique_study_id, participant_sex) |>
  count(participant_sex, sort = T) |> 
  mutate(perc = n / sum(n))
```


```{r descriptive_fig}
(country_fig = dat |> 
  distinct(unique_study_id, country) |> 
  mutate(country = ifelse(country == "USA", "USA", "Rest of the world")) |> 
  count(country, sort = T) |> 
  mutate(country = fct_rev(fct_reorder(factor(country), n)),
         perc = n / sum(n)) |>
  ggplot(aes(country, n, label = n, fill = country)) +
  geom_col() +
  theme_bw() +
  theme(axis.text = element_markdown(size = 12), 
        plot.title = element_markdown()) +
  scale_y_continuous(breaks = seq(0, 300, by = 100), limits = c(0, 300)) +
   scale_fill_manual(values = ggthemes::solarized_pal()(2)) +
  guides(fill = "none") +
  labs(title = "**a)** Number of Studies by Country",
       x = NULL, 
       y = "# of studies", 
       col = NULL))
  
(setting_fig = dat |> 
  distinct(unique_study_id, .keep_all = T) |> 
  count(setting, sort = T) |> 
  drop_na(setting) |> 
  mutate(perc = n / sum(n)) |>
  ggplot(aes(setting, n, fill = setting)) +
  geom_col() +
  scale_fill_manual(values = ggthemes::tableau_color_pal('Tableau 10')(6)) +
  labs(title = "**b)** Number of Studies by Setting",
       x = NULL, 
       y = "# of studies", 
       col = NULL) +
  theme_bw() +
    guides(fill = "none") +
  theme(axis.text = element_markdown(size = 12),
        plot.title = element_markdown()))


dat_participant_sex <- dat |> # participant sex lines
      mutate(participant_sex = ifelse(participant_sex %in% c("male and female in mixed groups", 
                                                             "male and female with group composition not specified", 
                                                             "male and female in separate groups"), 
                                      "mixed gender groups", 
                                      participant_sex)) |>
      distinct(unique_study_id, .keep_all = T) |>
      filter(participant_sex %in% c("mixed gender groups", "only male", "only female")) |>
      count(year, participant_sex) |>
      add_row(year = 1985, participant_sex = "mixed gender groups") |>
      complete(year, participant_sex, fill = list(n = 0)) |>
      mutate(participant_sex = str_to_title(participant_sex)) |>
  mutate(participant_sex = factor(participant_sex, levels = c("Mixed Gender Groups", "Only Male", "Only Female")))



(tt_gender_fig = dat_participant_sex |>
  ggplot(aes(year, n, col = participant_sex)) +
  geom_line(size = 2) +
  scale_x_continuous(
    limits = c(1985, 2018),
    breaks = c(1985, seq(1985, 2020, by = 5), 2018)
  ) +
  scale_color_manual(values = ggthemes::palette_pander(3)) +
  theme_bw() +
  theme(
    axis.text = element_markdown(size = 12), 
    legend.text = element_markdown(size = 12),
    plot.title = element_markdown(),
    legend.position = "bottom"
  ) +
  labs(
    title = "**c)** Number of Studies Over Time by Group Gender (1985-2018)",
    x = NULL,
    y = "# of studies",
    col = NULL
  ))

country_fig / setting_fig / tt_gender_fig

ggsave("results/descriptive.pdf", width = 7, height = 7)
```


## Zeitgeist Programs



Most of the studies we identified in the first 15 years were conducted by students coming from various disciplines including psychology, educational psychology, and counseling psychology. The majority of these studies are laboratory studies (n = 107) as opposed to field studies (n = 78) that encompass the larger programmatic evaluations that dominate the next generation of studies.
```{r}
dat |> 
  filter(between(year, 1985, 2000)) |> 
  distinct(unique_study_id, lab_field, publication_type) |> 
  count(lab_field)


dat |> 
  filter(between(year, 1985, 2000)) |> 
  distinct(unique_paper_id, author, year, paper_title, lab_field) |> 
  View()
  write_csv("first_15years.csv")

dat |> 
  filter(between(year, 1985, 2000)) |> 
  distinct(unique_paper_id) |> 
  nrow()


dat |> 
  mutate(early = between(year, 1985, 2000)) |> 
  distinct(unique_paper_id, .keep_all = T) |> 
  summarise(perc_early = mean(early))

dat |> 
  filter(between(year, 1985, 2000)) |> 
  distinct(unique_study_id, publication_type) |> 
  count(publication_type) |> 
adorn_totals()


dat |> 
  select(scale_name, behavior_type) |> 
  filter(behavior_type == "Attitude") |> 
  mutate(myth_scale = str_detect(str_to_lower(scale_name), "myth")) |> 
  group_by(myth_scale) |> 
  summarise(n = n())
  
```








```{r}
dat |> 
  distinct(unique_study_id, .keep_all = T) |> 
  count(setting, sort = T) |> 
  mutate(perc = n / sum(n)) |> 
  janitor::adorn_totals()
```

```{r}
dat |> 
  distinct(unique_paper_id, .keep_all = T) |> 
  count(setting, sort = T) |> 
  mutate(perc = n / sum(n)) |> 
  janitor::adorn_totals()
```

```{r}
dat |> 
    mutate(participant_sex = ifelse(participant_sex %in% c("male and female in mixed groups", 
                                                           "male and female with group composition not specified", 
                                                           "male and female in separate groups"), 
                                    "mixed gender groups",
                                    participant_sex)) |> 
  distinct(unique_paper_id, .keep_all = T) |> 
  count(participant_sex, sort = T) |> 
  mutate(perc = n / sum(n)) |> 
  janitor::adorn_totals()
```








```{r}
dat %>%
  drop_na(study_design) |> 
  ggplot(aes(x = se_d, y = d)) +
  geom_point(aes(
      color = behavior_type,
      shape = study_design),
    size = 3
  ) +
  geom_smooth(
    method = "lm",
    se = F,
    size = 2
  ) +
  #ggtitle("Relationship between effect sizes and standard errors") +
  labs(
    x = "Standard errors",
    y = "Effect size",
    color = "Outcome type",
    shape = "Study Design"
  ) +
  theme_bw() +
  theme(
    axis.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.position = "bottom",
    legend.box = "vertical"
  )

ggsave("../results/d_se.pdf", height = 5)

```


```{r}
dat %>% 
  filter(has_both == 'both') %>% 
  drop_na(study_design) |> 
  group_by(author, year, study_design, unique_study_id, scale_type) %>%
  #filter(delay == min(delay)) |> 
  summarise(mean_d = mean(d), 
         mean_var_d = mean(var_d), 
         mean_se_d = mean(se_d)) %>% 
  pivot_wider(id_cols = c(author, year, unique_study_id, study_design),
    names_from = c(scale_type), 
    values_from = c(mean_d, mean_var_d, mean_se_d)) %>%
  ggplot(aes(x = mean_d_attitudes,
             y = mean_d_behavior)) + 
  geom_point(aes(color = study_design),
             size = 3) + 
  geom_abline(slope = 1, 
              lty = 'dashed',
              size = 2) +
  geom_smooth(lty = "dashed", 
              method = "lm", 
              se = FALSE,
              color = 'grey',
              size = 2) +  
  scale_x_continuous(breaks = seq(-.5, 1.5, by = .5), limits = c(-.5,1.6)) +
  scale_y_continuous(breaks = seq(-.5, 1.5, by = .5), limits = c(-.5,1.6)) +
  labs(x = "Effect size (attitudes)",
       y = "Effect size (behaviors)",
       color = "Study Design") +
  guides(color = guide_legend(title = "Study Design")) + 
  theme_bw() +
    theme(
    axis.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.position = "bottom",
    legend.box = "vertical"
  )

ggsave("../results/att_beh_corr.pdf", width = 7, height = 7)
```


```{r}
dat %>%
  filter(behavior_type != "Attitude") |> 
  distinct(unique_study_id, year, behavior_type) |> 
  count(year, behavior_type) |> 
  add_row(year = 1985:1990, behavior_type = "Involvement") |> # start at 0 for all behaviors. here i use arbitrary behavior 
  complete(year, behavior_type, fill = list(n = 0)) |> 
  ggplot(aes(x = year, y = n, color = behavior_type)) +
  geom_line(size = 3) + 
  labs(title = "**a)** Number of Studies by Country",
       x = NULL, 
       y = "# of studies", 
       col = NULL) +
  scale_x_continuous(
    limits = c(1985, 2018),
    breaks = c(1985, seq(1985, 2020, by = 5), 2018)
  ) +
  theme_bw() +
    theme(
    axis.text = element_text(size = 12),
    legend.text = element_text(size = 12),
    legend.position = "bottom",
    legend.box = "vertical"
  )

```


Table XX details the distribution of behavioral outcomes within studies that employ observational designs (i.e., quasi-experimental and observational studies) and randomized designs (i.e., experiments and horse-race experiments). 
```{r}

dat |> 
  filter(scale_type == "behavior") |> 
  distinct(unique_study_id, study_design, behavior_type) |> 
  count(study_design, behavior_type) |> 
  pivot_wider(values_from = n, id_cols = behavior_type, names_from = study_design, values_fill = 0) |> 
  janitor::adorn_totals() |> 
  kable(format = "latex", booktabs = T)
```


We recovered XXX manuscripts and XXX studies from our search that qualified methodologically and theoretically.

```{r}
dat %>% 
  select(unique_study_id, unique_paper_id) %>% 
  summarise(n_papers = n_distinct(unique_paper_id),
            n_studies = n_distinct(unique_study_id))
```



### Overview of Studies in the Meta-Analytic Database

```{r }
dat |> 
  select(contains("n_")) |> 
  View()

# average N?
mean(dat$n_t_post) + mean(dat$n_c_post)
mean(dat$n_t_pre, na.rm = T) + mean(dat$n_c_pre, na.rm = T)

# participant sex
table(dat$condition_gender)

## intervention length
mean(dat$intervention_length, na.rm = T)
quantile(dat$intervention_length, probs = seq(0, 1, by = 0.2), na.rm = TRUE)
```

### Meta-Analytic Results

(see 3-sa-meta.Rmd)


We found XX studies that measured self-reported behavior.
```{r}
dat %>% 
  select(unique_study_id, scale_type) %>% 
  group_by(scale_type) %>% 
  summarise(n_unique_studies = n_distinct(unique_study_id)) 
```

XX of these studies measured behavior only in the immediate aftermath of the intervention, while xx included long-term measures.  
```{r}
dat %>% 
  filter(scale_type == "behavior") %>% 
  select(unique_study_id, delay) %>% 
  drop_na(delay) %>% 
  group_by(unique_study_id) %>% 
  mutate(max_delay = max(delay),
         only_short_term = max_delay == 0) %>% 
  count(only_short_term) %>% 
  ungroup() %>% 
  count(only_short_term)
```

To do so, we break down our dataset according to four types of study designs: experimental studies, quasi experimental studies, and observational studies. as presented in Table X, 
```{r}
dat %>% 
  select(unique_study_id, scale_type, study_design, d) %>% 
  filter(scale_type == "behavior") %>% 
  group_by(unique_study_id, study_design) %>% 
  summarise(mean_d_by_study_x_design = mean(d)) %>% 
  group_by(study_design) %>% 
  summarise(n = n(),
            mean_d_by_design = mean(mean_d_by_study_x_design)) %>% 
  kable(digits = 2, format = "latex", booktabs = T) %>%
  kableExtra::kable_styling() 
```

```{r}
dat |> 
  filter(scale_type == "attitudes") |> 
  distinct(unique_study_id, scale_name) |> 
  count(scale_name, sort = T) |> 
  View()
```

how many studies evaluate rape myths?
```{r rape_myth_outcome_prevalence}
dat %>%
  group_by(unique_study_id) %>%
  summarise(
    myth_var = any(str_detect(scale_name, "myth|IRMA|illinois"))
  ) %>%
  summarise(
    myth_count = sum(myth_var),
    no_myth_count = sum(!myth_var)
  )

```

what's the distribution of outcome types for bystander interventions

```{r bystander_dv_count}

# filter based on mentioning bystander in either title, description, 
# intervention name, or program name, or have a stated purpose of "4" (bystander)
bystander_dat <- dat %>%
  filter(
    str_detect(paper_title, "bystander") |
      str_detect(brief_description_of_the_intervention, "bystander") |
      str_detect(intervention_name, "bystander") |
      str_detect(program_name, "bystander") |
      str_detect(stated_purpose, "4")) %>%
    select(author, year, paper_title, unique_study_id, study_design,
           d, var_d, se_d, 
           behavior_type, has_both) %>%
  mutate(perp_vict_grouped = case_when(
    behavior_type == 'Victimization' | behavior_type == 'Perpetration' ~ 'perp_vict',
    behavior_type == 'Involvement' ~ 'involvement',
    behavior_type == 'Attitude' ~ 'Attitude',
    behavior_type == 'Bystander' ~ 'Bystander'))

bystander_dat %>%  study_count()

bystander_dat %>% group_by(behavior_type) %>% study_count()

bystander_dat %>% group_by(has_both) %>% study_count()

bystander_dat %>% filter(behavior_type != 'Involvement') %>% 
  split(.$perp_vict_grouped) %>% 
  map(.f = map_robust)

table(bystander_dat$behavior_type)    

# count studies that measure #just bystander behaviors
bystander_dat %>%
  filter(has_both != 'attitudes') %>% group_by(perp_vict_grouped) %>% study_count()

# double-check
bystander_dat_not_just_atts %>% 
  group_by(unique_study_id) %>%
  filter('Bystander' %in% behavior_type & !'perp_vict' %in% perp_vict_grouped) %>% ungroup() %>% study_count()


# what kind of effect sizes are we talking about? 
bystander_dat %>% filter(behavior_type != 'Involvement') %>% split(.$behavior_type) %>% map(map_robust)

# group perp and vict outcomes together

bystander_dat %>% filter(behavior_type != 'Involvement') %>% split(.$perp_vict_grouped) %>% map(map_robust)


# bystander interventions are a product of their time and place
bystander_dat %>% group_by(unique_study_id) %>% slice(1) %>% ungroup() %>%
  ggplot(aes(x = year)) +
  geom_line(stat = 'count', color = 'light blue') + 
  labs(x = "Year", 
       y = "Count", 
       title = "Bystander interventions over time") +
  # scale_x_date(date_breaks = "2 years") +
  scale_x_continuous(n.breaks = 20) +
  scale_y_continuous(n.breaks = 15) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))

## BTW an alternate way to do this
dat %>%
  group_by(unique_study_id) %>%
  summarise(
    bystander_count = ifelse(
      any(
        str_detect(c(
          brief_description_of_the_intervention, 
          intervention_name, program_name, paper_title), "bystander")) |
        any(str_detect(stated_purpose, "4")),
      TRUE, FALSE)
  ) %>% 
  summarise(
    bystander = sum(ifelse(is.na(bystander_count), FALSE, bystander_count)),
    no_bystander = sum(ifelse(is.na(bystander_count), TRUE, !bystander_count))
  )




```